\documentclass[11pt]{article}
\usepackage[compact]{titlesec}

\textheight 9.5in
\textwidth 6.5in
\topmargin -0.5in
\oddsidemargin 0in
\evensidemargin 0in
%\headheight 0in
%\footheight 0in
\parindent 0in

\begin{document}
\pagestyle{empty}
%\rightline{\today}
%\bigskipx1x1
%
%\centerline{\Large\bf
%{\Large\bf M}ordecai-{\Large\bf M}ark {\Large\bf M}ac {\Large\bf L}ow}
\centerline{\bf Mordecai-Mark Mac Low}
\smallskip

\paragraph{Professional Preparation}
\begin{itemize} %}{lp{5.5in}}               
\setlength{\itemsep}{-\parsep}
\setlength{\topsep}{-\parsep}
\setlength{\partopsep}{-\parsep}
% & \\ 	Stuyvesant High School, NYC:  graduated 1979 
\item  Princeton University:  A. B., Physics, 1983
%                  \hspace*{0.15in}(Senior Thesis advisor: Joseph
%		Taylor)} \
\item University of Colorado at Boulder:  
                          M.A., Physics, 1985;  Ph.D., Physics, 1989
%                  \hspace*{0.15in}(Dissertation advisor: Richard McCray)} 

\item {NRC Postdoctoral Fellow, NASA Ames,  1989--1990}  
\item {Research Assoc., Center for Star Formation Studies, UC Berkeley,  1991--1992}  
\item {Research Assoc.,  Dept. of Astronomy \& Astrophysics, U. Chicago,  1992--1995} 
\end{itemize}
%\bigskip
%\bigskip

\paragraph{Appointments}
\begin{itemize}
\setlength{\itemsep}{-\parsep}
\setlength{\topsep}{-\parsep}
\setlength{\partopsep}{-\parsep}
%\begin{tabular}{lp{4.1in}}
%{\it Appointments :} & 
\item \parbox{1.5in}{Jul 2007 --   } \parbox{5in}{
             Curator, Dept.\ of Astrophys., Amer.\ Museum of
             Natural History (AMNH)} 
\item \parbox{1.5in}{Jul 2007 --  } \parbox{5in}{
             Adjunct Professor, Dept.\ of Astronomy,
Columbia University} 
\item \parbox{1.5in}{Apr 2012 --   }\parbox{5in}{
             Visiting Research Professor, Dept.\ of Physics,
Drexel University} 
\item \parbox{1.5in}{Jul 2007 -- Jun 2012  }\parbox{5in}{
             Chair, Division of Physical Sciences, AMNH}  
\item \parbox{1.5in}{Jul 2005 -- Jun 2012  }\parbox{5in}{
             Curator-in-Charge, Dept.\ of Astrophys., AMNH}  
\item \parbox{1.5in}{Jul 2002 -- Jun 2007} \parbox{4.0in}{
             Associate Curator, Dept.\ of Astrophys., AMNH}  
\item \parbox{1.5in}{May 1999  -- Jun 2002}  \parbox{4.0in}{
             Assistant Curator, Dept.\ of Astrophys., AMNH} 
\item \parbox{1.5in}{Sep 1995  --  Apr 1999} \parbox{4.0in}{
             Scientist, Max Planck Institute for Astronomy} 
%
% \item \parbox{1.5in}{Jan 1994  --  Aug 1995} \parbox{4.0in}{
%              Rsch. Assoc., Dept. of Astronomy, UIUC} 
% \item \parbox{1.5in}{Sep 1992  --  Aug 1995} \parbox{4.0in}{
%              Rsch. Assoc.,  Dept. of Astron.\ \& Astrophys., U. 
% Chicago} 
% \item \parbox{1.5in}{Jan 1991  --  Aug 1992} \parbox{4.0in}{
%      Rsch. Assoc., Ctr.\ for Star Form.\ Studies, UC Berkeley}  
% \item \parbox{1.5in}{Jan 1989  --  Dec 1990} \parbox{4.0in}{
%      NRC Postdoctoral Fellow, NASA Ames} 
% \item \parbox{1.5in}{Sep 1983  --  Dec 1988} \parbox{4.0in}{
%      Rsch Asst., JILA,   U. of Colorado and NBS}  
%Summer 1984}& \parbox{4.0in}{Programmer, Space Astronomy 
%     Laboratory, University of Wisconsin at Madison} 
%& 
%Summer 1982 \parbox{4.0in}{Undergraduate Research Fellow,
%      Division of Geological and Planetary Sciences, California Institute of 
%      Technology} 
\end{itemize}
%\vspace{-15pt}
\paragraph{Five Relevant Products}
\begin{enumerate}
%\vspace{-9pt}
\setlength{\itemsep}{-\parsep}
\setlength{\topsep}{-2\parsep}
\setlength{\partopsep}{-2\parsep}
\item ``Starburst-driven Mass Loss from Dwarf Galaxies: Efficiency
     and Metal Ejection'', Mac Low, M.-M., and Ferrara, A. 1999, 
     Ap.\ J., 513, 142.
\item ``Dependence of Interstellar Turbulent Pressure on Supernova
  Rate,'' Joung, M. R., Mac Low, M.-M., \& Bryan, G. L. 2009,
  Astrophys.\ J., 704, 137--149.
\item ``Vertical structure of a supernova-driven turbulent, magnetized
  interstellar medium,'' 2012, Hill, A. S., Joung, M. R., Mac Low,
  M.-M., Benjamin, R. A., Haffner, L. M., Klingenberg, C., \& Waagan,
  K. Astrophys.\ J., 750, 104 (19 pp).  (Erratum: 761, 189).
\item ``Launching Cosmic Ray-Driven Outflows From the Magnetized
  Interstellar Medium,'' Girichidis, P., Naab, T., Walch, S., Hanasz,
  M., Mac Low, M.-M., Ostriker, J. P., Gatto, A., Peters, T.,
  W\"unsch, R., Glover, S. C. O., Klessen, R. S., Clark, P. C., \&
  Baczynski, C. 2015, ApJ, 816, L19 (6 pp).
\item ``Gravitational Contraction Versus Supernova Driving and the
  Origin of the Velocity Dispersion-size Relation in Molecular
  Clouds,'' Ib\'a\~nez-Mej\'{\i}a, J. C., Mac Low, M.-M., Baczynski,
  C., \& Klessen, R. S. 2016, Astrophys.\ J., 824, 41 (15 pp).

\end{enumerate}
%\vspace{-20pt}
\paragraph{Five Other Significant Products}
\begin{enumerate}
%\vspace{-9pt}
\setlength{\itemsep}{-\parsep}
\setlength{\topsep}{-\parsep}
\item ``Superbubbles in Disk Galaxies,'' Mac Low, M.-M., and McCray, R.  1988,
Astrophys.\ J., 324, 776--785.
\item ``Kinetic Energy Decay Rates of Supersonic and Super-Alfv\'enic
Turbulence in Star-Forming Clouds,'' Mac Low, M.-M., Klessen, R. S.,
Burkert, A., and Smith, M. D. 1998, Phys. Rev. Lett., 80, 2754--2757.
\item ``The Control of Star Formation by Supersonic Turbulence'', Mac
Low, M.-M., \& Klessen, R. S., 2004, Rev. Mod. Phys., 76, 125. 
\item ``Rapid Planetesimal Formation in Turbulent Circumstellar Discs,''
Johansen, A., Oishi, J. S., Mac Low, M.-M., Klahr, H., Henning, Th.,
\& Youdin, A. 2007, Nature, 448, 1022.
\item ``From Gas to Stars Over Cosmic Time,'' Mac Low, M.-M. 2013,
  Science, 340, 1229229 (8 pp).

\end{enumerate}
%\vspace{-20pt}
\paragraph{Five Synergistic Activities}
\begin{itemize}
%\vspace{-9pt}
\setlength{\itemsep}{-\parsep}
\setlength{\topsep}{-\parsep}
\setlength{\partopsep}{-\parsep}
\item curator of 2013 Hayden Planetarium Space Show
  ``Dark Universe,'' covering $\Lambda$CDM cosmology. 
\item Lead curator of 2009 Space Show, ``Journey to the Stars,''
  covering topics of primordial and modern star formation and stellar evolution.
 Shows play at Hayden for $\sim$3 yr,
  with $\sim$1M viewers/yr, \& licensed for $> 10$ yr to
  40 planetaria in US \& abroad, with total for all shows of $> 10$M viewers/yr.
\item co-PI and
  Prof., MA in Teaching, 
  Earth Science teacher education degree program at the American
  Museum of Natural History, teaching Space Science course. Over 15
  graduates per year committed to teach 4 yr in high needs public
  schools.
\item Member of Congressionally mandated Astronomy \& Astrophysics
  Advisory Comm. (2011-2014), vice-chair 2013-2014.
\item {\em Media:} Interviews and visualizations in national and international
media including CNN, NBC, NHK, {\em New York Times, Time, Newsweek,
Scientific American}
\end{itemize}

\end{document}

\vspace{-20pt}
\paragraph{Collaborators in Last Four Years}

% {\footnotesize Marcel Agueros (Columbia), Charlee Amason (Agnes Scott),
%   Javier Ballesteros-Paredes (UNAM), Robi Banerjee (U. Hamburg),
%   Robert Benjamin (UW Whitewater), Christian Baczynski (St. Andrews),
%   A. Bischoff (U. M\"unster), Martin Bizarro (U. Copenhagen/NHMD),
%   Alberto Bolatto (U Md.), Howard E. Bond (Penn State/STScI), Aaron
%   Boley (U. Brit. Columbia), Greg Bryan
%   (Columbia), Katie Butler (Agnes Scott), Paul C. Clark (Cardiff U.),
%   David Collins (Florida State), Julie Contino (AMNH), Natasha
%   Cooke-Nieves (AMNH), Paula D'Alessio (deceased), Orsola De Marco
%   (Macquarie), Christopher De Pree (Agnes Scott), Steven Diehl
%   (unaffil.), Clare Dobbs (Exeter), Cornelis Dullemond
%   (ITA/ZAH), Denton Ebel (AMNH),
%   Christoph Federrath (ANU), Kennet Flores (AMNH), K. E. Saavik Ford
%   (CUNY BMCC/AMNH), Jonathan M. Friedrich (Fordham), Christopher Fryer
%   (LANL), Yasuo Fukui (Nagoya), Catherine A. Garland (Uncommon
%   Charter HS), Andrea Gatto (MPA), Roberto Galv\'an-Madrid (UNAM),
%   Philipp Girichidis (MPA),
%   Simon C. O. Glover (ITA/ZAH), Patrick Godon (Villanova), Miller Goss
%   (NRAO), Jana Grcevich (AMNH), R. Guzm\'an (U. Florida), L. Matthew
%   Haffner (UW Madison), Sebastian Haid (U. Cologne), Micha\l{} Hanasz
%   (Copernicus U., Torun), George Harlow (AMNH), David B. Henley
%   (U. Ga.), Falk Herwig (Victoria), Mark Heyer (UMass), Alex S. Hill
%   (Haverford), Brandon Horn (unaffil.), Elaine Howes (AMNH),
%   Alexander Hubbard (AMNH), Juan Ib\'a\~nez-Mej\'{\i}a
%   (AMNH/U. Heidelberg), Anders Johansen (U. Lund), Kathryn Johnston
%   (Columbia), Mookwang R. Joung (Columbia), T. Kelling
%   (U. Duisberg-Essen), Eric Keto (CfA), Rosamond
%   Kinzler (AMNH), Pamela Klaassen (ROE), Ralf S. Klessen (ITA/ZAH),
%   Christian Klingenberg (U. W\"urzburg), K. Kreckel (MPIA), Mark
%   Krumholz (UCSC), Kyujin Kwak (U. Ga.), Pedro Lacerda (MPI Solar
%   System), Sebastien Lepine (Georgia State), Christoph Loesche (U. Duisberg-Essen), Wladimir Lyra (CSU
%   Northridge), Maritza Macdonald (AMNH),  Stephen McMillan (Drexel), Colin McNally (NBIA), Jason Maron
%   (unaffil.), Kristen Menou (Toronto), Ashley
%   Monsrud (Agnes Scott), Thorsten Naab (MPA), Patricia Nadeau (AMNH),
%   Jeffrey Oishi (AMNH/SUNY Farmingdale), Eve Ostriker (Princeton),
%   Jeremiah P. Ostriker (Princeton/Columbia), Timothy Paglione (CUNY York/AMNH), Ashley Pagnotta
%   (AMNH), Jean-Claude Passy (AIfA, Bonn), Thomas Peters (MPA), D. J. Pisano (WVU), Dina Prialnik (Tel-Aviv
%   U.), K. Rabidoux (WVU), Alexander J. W. Richert (Penn State), Dennis
%   Robbins (CUNY Hunter), Gabriel Rockefeller (LANL), Zsolt S\'andor
%   (Vienna), Bradley E. Schaefer (LSU), Martin Schr\"on (Helmholtz
%   UFZ), Jocelyn Sessa (AMNH), Michael Shara (AMNH), Sanjib Sharma
%   (U. Sydney), Robin Shelton (U. Ga.), Christine M. Simpson (HITS),
%   Edward Sion (Villanova), Britton D. Smith (MSU), Michael D. Smith
%   (U. Kent), Moeko Tamura (Barnard), Jayashree Toraskar (AMNH), Jason Tumlinson (STScI), Neal Turner (JPL), Gokce
%   Ustunisik (AMNH), Enrique V\'azquez-Semadeni (UNAM), Knut Waagan
%   (U. Wash., Seattle), Stefanie Walch (U. Cologne), James D. Webster
%   (AMNH), David Wilner (CfA), Joshua Wall (Drexel), Robert E. Williams
%   (STScI), Kenneth Wood (St. Andrews), Richard W\"unsch (Acad. Czech Rep.), Gerhard Wurm
%   (U. Duisberg-Essen), Chao-Chin Yang (Lund), Marion Zachowski (AMNH),
%   Nasser Zirakparvar (AMNH), David Zurek (AMNH)} \vspace{-10pt}

{\small M. Ag\"ueros (Columbia), C. Amason (Agnes Scott),
  J. Ballesteros-Paredes (UNAM), R. Banerjee (U. Hamburg),
  R. Benjamin (UW Whitewater), C. Baczynski (St. Andrews),
  A. Bischoff (U. M\"unster), M. Bizarro (U. Copenhagen/NHMD),
  A. Bolatto (U Md.), H. E. Bond (Penn State/STScI), A.
  Boley (U. Brit. Columbia), G. Bryan
  (Columbia), K. Butler (Agnes Scott), P. C. Clark (Cardiff U.),
  D. Collins (Florida State), J. Contino (AMNH), N.
  Cooke-Nieves (AMNH), P. D'Alessio (deceased), O. De Marco
  (Macquarie), C. De Pree (Agnes Scott), S. Diehl
  (unaffil.), C. Dobbs (Exeter), C. Dullemond
  (ITA/ZAH), D. Ebel (AMNH),
  C. Federrath (ANU), K. Flores (AMNH), K. E. Saavik Ford
  (CUNY BMCC/AMNH), J. M. Friedrich (Fordham), C. Fryer
  (LANL), Y. Fukui (Nagoya), C. A. Garland (Uncommon
  Charter HS), A. Gatto (MPA), R. Galv\'an-Madrid (UNAM),
  P. Girichidis (MPA),
  S. C. O. Glover (ITA/ZAH), P. Godon (Villanova), M. Goss
  (NRAO), J. Grcevich (AMNH), R. Guzm\'an (U. Florida), L. M.
  Haffner (UW Madison), S. Haid (U. Cologne), M. Hanasz
  (Copernicus U., Torun), G. Harlow (AMNH), D. B. Henley
  (U. Ga.), F. Herwig (Victoria), M. Heyer (UMass), A. S. Hill
  (Haverford), B. Horn (unaffil.), E. Howes (AMNH),
  A. Hubbard (AMNH), J. C. Ib\'a\~nez-Mej\'{\i}a
  (AMNH/U. Heidelberg), A. Johansen (U. Lund), K. Johnston
  (Columbia), M. R. Joung (Columbia), T. Kelling
  (U. Duisberg-Essen), E. Keto (CfA), R.
  Kinzler (AMNH), P. Klaassen (ROE), R. S. Klessen (ITA/ZAH),
  C. Klingenberg (U. W\"urzburg), K. Kreckel (MPIA), M.
  Krumholz (UCSC), K. Kwak (U. Ga.), P. Lacerda (MPI Solar
  System), S. Lepine (Georgia State), C. Loesche (U. Duisberg-Essen), W. Lyra (CSU
  Northridge), M. Macdonald (AMNH),  S. McMillan (Drexel), C. McNally (NBIA), J. Maron
  (unaffil.), K. Menou (Toronto), A.
  Monsrud (Agnes Scott), T. Naab (MPA), P. Nadeau (AMNH),
  J. Oishi (AMNH/SUNY Farmingdale), E. Ostriker (Princeton),
  J. P. Ostriker (Princeton/Columbia), T. Paglione (CUNY York/AMNH), A. Pagnotta
  (AMNH), J.-C. Passy (AIfA, Bonn), T. Peters (MPA), D. J. Pisano (WVU), D. Prialnik (Tel-Aviv
  U.), K. Rabidoux (WVU), Alexander J. W. Richert (Penn State), D.
  Robbins (CUNY Hunter), G. Rockefeller (LANL), Z. S\'andor
  (Vienna), B. E. Schaefer (LSU), M. Schr\"on (Helmholtz
  UFZ), J. Sessa (AMNH), M. Shara (AMNH), S. Sharma
  (U. Sydney), R. Shelton (U. Ga.), C. M. Simpson (HITS),
  E. Sion (Villanova), B. D. Smith (MSU), M. D. Smith
  (U. Kent), M. Tamura (Barnard), J. Toraskar (AMNH), J. Tumlinson (STScI), N. Turner (JPL), G.
  Ustunisik (AMNH), E. V\'azquez-Semadeni (UNAM), K. Waagan
  (U. Wash., Seattle), S. Walch (U. Cologne), J. D. Webster
  (AMNH), D. Wilner (CfA), J. Wall (Drexel), R. E. Williams
  (STScI), K. Wood (St. Andrews), R. W\"unsch (Acad. Czech Rep.), G. Wurm
  (U. Duisberg-Essen), C.-C. Yang (Lund), M. Zachowski (AMNH),
  N. Zirakparvar (AMNH), D. Zurek (AMNH)} \vspace{-10pt}

\vspace{-5pt}
\paragraph{Advisors:} J. Taylor
(Princeton; undergrad), Richard McCray (U. Colo.\ (Boulder; grad),
David Hollenbach (NASA Ames; postdoc), Christopher McKee (UC
Berkeley; postdoc), Arieh K\"onigl (Chicago; postdoc)
\vspace{-10pt}
\paragraph{Students:} Guillermo Garc\'{\i}a-Segura (UNAM), Akimi  Fujita
(Shinshu U.), Mookwang R.  Joung (Columbia),
Yuexing Li (Penn State), Jeffrey Oishi (SUNY Farmingdale/AMNH), Chao-Chin Yang (U. Lund),
Colin McNally (NBIA, Copenhagen), Jean-Claude Passy (AIfA, Bonn), Brandon Horn
(unaffil.). Juan Iba\~nez-Mej\'{\i}a (AMNH/U. Heidelberg), Joshua Wall (Drexel)
\vspace{-10pt}

\paragraph{Postdocs:} Javier Ballesteros-Paredes (UNAM), Jillian
Bellovary (AMNH), Paola D'Alessio (deceased),
Miguel Avillez (U. Evora), Simon C. O. Glover (ITA/ZAH), Wladimir Lyra
(CSU Northridge), Jason Maron (unaffil.), Jana Grcevich (AMNH), Alexander Hubbard (AMNH),
H\'ector Arce (Yale)

\end{document}